\documentclass{article}\usepackage{amsmath}\begin{document}\title{Simplex Solver}\maketitle\begin{flushleft}\textbf{Problem}\end{flushleft}\begin{flushleft}Given the following linear system and objective function, find the optimal solution.\end{flushleft}\begin{equation*}\max{ 9x_1 + 10x_2 + 11x_3 } \\ \end{equation*}\[\left\{\begin{array}{c} x_1 + 2x_2 + 3x_3 \leq 7 \\  4x_1 + 5x_2 + 6x_3 \leq 8 \\ \end{array}\right.\]\begin{flushleft}\textbf{Solution}\end{flushleft}\begin{flushleft}Add slack variables to turn all inequalities to equalities.\end{flushleft}\[\left\{\begin{array}{c} x_1 + 2x_2 + 3x_3 + s_1 = 7 \\  4x_1 + 5x_2 + 6x_3 + s_2 = 8 \\ \end{array}\right.\]\begin{flushleft}Create the initial tableau of the new linear system.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{ccccc|c}x_1 &x_2 &x_3 &s_1 &s_2 &b \\ \hline1 & 2 & 3 & 1 & 0 & 7 \\4 & 5 & 6 & 0 & 1 & 8 \\ \hline-9 & -10 & -11 & 0 & 0 & 0 \\\end{array}\end{bmatrix}\begin{array}{c}\\s_1 \\s_2 \\\\\end{array}\end{equation*}\begin{flushleft}There are negative elements in the bottom row, so the current solution is not optimal. Thus, pivot to improve the current solution. The entering variable is $x_3$ and the departing variable is $s_2$.\end{flushleft}\begin{flushleft}Perform elementary row operations until the pivot element is 1 and all other elements in the entering column are 0.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{ccccc|c}x_1 &x_2 &x_3 &s_1 &s_2 &b \\ \hline-1 & -1/2 & 0 & 1 & -1/2 & 3 \\2/3 & 5/6 & 1 & 0 & 1/6 & 4/3 \\ \hline-5/3 & -5/6 & 0 & 0 & 11/6 & 44/3 \\\end{array}\end{bmatrix}\begin{array}{c}\\s_1 \\x_3 \\\\\end{array}\end{equation*}\begin{flushleft}There are negative elements in the bottom row, so the current solution is not optimal. Thus, pivot to improve the current solution. The entering variable is $x_1$ and the departing variable is $x_3$.\end{flushleft}\begin{flushleft}Perform elementary row operations until the pivot element is 1 and all other elements in the entering column are 0.\end{flushleft}\begin{equation*}\begin{bmatrix}\begin{array}{ccccc|c}x_1 &x_2 &x_3 &s_1 &s_2 &b \\ \hline0 & 3/4 & 3/2 & 1 & -1/4 & 5 \\1 & 5/4 & 3/2 & 0 & 1/4 & 2 \\ \hline0 & 5/4 & 5/2 & 0 & 9/4 & 18 \\\end{array}\end{bmatrix}\begin{array}{c}\\s_1 \\x_1 \\\\\end{array}\end{equation*}\begin{flushleft}There are no negative elements in the bottom row, so we know the solution is optimal. Thus, the solution is: \end{flushleft}\begin{equation*}s_1 = 5, s_2 = 0, x_1 = 2, x_2 = 0, x_3 = 0, z = 18\end{equation*}\end{document}